APPENDIX: [Insert Paper Title Here]

### 2021-11-18 inst/other_docs/appendix.Rmd
dsfsfs

---
title: "APPENDIX: [Insert Paper Title Here]"
# author:
# - name: Steven V. Miller
#   affiliation: Clemson University
#   email: svmille@clemson.edu
# thanks: "This is a work in progress. Feedback welcome: svmille@clemson.edu."
# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`"
# biblio-style: apsr
geometry: margin=1in
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
keywords: ""
endnotes: FALSE
# csl: inst/jpr.csl
mainfont: cochineal
# sansfont: Linux Biolinum O
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
appendix: TRUE
appendixletter: "A"
pandocparas: FALSE
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
linkcolor: black
header-includes:
  - \usepackage{longtable}
  - \usepackage{csquotes}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \renewcommand{\thepage}{A-\arabic{page}}
---

>>>>

---
title: "APPENDIX: [Insert Paper Title Here]"
author:
- name: Carl Sagan
  affiliation: Cornell University & the Cosmos
- name: Steven V. Miller
  affiliation: Clemson University
# thanks: "This is a work in progress. Feedback welcome: svmille@clemson.edu."
# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`"
# biblio-style: apsr
geometry: margin=1in
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
keywords: ""
endnotes: FALSE
# csl: inst/jpr.csl
mainfont: cochineal
# sansfont: Linux Biolinum O
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
appendix: TRUE
appendixletter: "A"
pandocparas: FALSE
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
linkcolor: black
header-includes:
  - \usepackage{longtable}
  - \usepackage{csquotes}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
  - \usepackage{setspace}
  - \renewcommand{\thepage}{A-\arabic{page}}
---
